Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2020-06-10 man/figures/0_figures_ecosystems.Rmd
update legend figures

**Figure 2**. Schema of the metrics and analysis used in the manuscript (see Material and methods for details) and their relation with the aims (numbers in grey circles) of our study (see Introduction). The severe drought events since 1901 were identified using SPEI-12 and regional climatic data. They were characterized in terms of duration, severity, intensity. Resilience metrics of BAI were computed for the most severe drought events since 1950, and the relationship of them to the severity of the drought were explored. For 2005 and 2012 drought events we also compute resilience metrics. A comparison of EVI and BAI resilience metrics for the 2005 and 2012 drought events was conducted among Q. pyrenaica populations.

@@

#####
**Figure 1**
![](../../out/fig/geomap/mapa_situacion_v2.jpg){height=750px} 
##### 
**Figure 2.**
![](../../man/figures/schema_methods/propuesta_esquema2.jpg)

>>>>

**Figure 2**. Schema of the different metrics (a) and analyses (b) used in the manuscript (see Material and methods for details). The severe drought events since 1901 were identified using SPEI-12 and characterized in terms of duration, severity and intensity. Climate impacts on vegetation were assessed for greenness and tree-growth. Non climatic disturbances on vegetation were quantified using growth changes on tree growth (% GC) and were also related with anthropogenic alterations inferred from review of historical documents. Responses of vegetation to disturbances were explored in the short- and the long-term using resilience metrics and temporal trends respectively for both EVI and BAI. Resilience metrics of BAI were computed for the eight most severe drought events since 1950, and their relationship with drought severity were explored. For the 2005 and 2012 drought events we also compared EVI and BAI resilience metrics among the three *Q. pyrenaica* populations.

@@

#####
**Figure 1**
![](../../out/fig/geomap/mapa_situacion_v2.jpg){height=750px} 
##### 
**Figure 2.**
![](../../man/figures/schema_methods/schema_analysisv3@1,5x.jpg)0
